### 2025-03-10 chapters/dissertation-tap.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his methodical problem solving strategies, depth and 
breadth of knowledge have been invaluable sources of inspiration for me as well as 
motivating myself to strive towards those ideals. I would also like to thank members of my committee, 
from the University of Delaware and Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

Listing everyone I am grateful for who have provided me non-academic support would be too long for this page 
although I shall try to summarize this. I am grateful to my family, with whom I may not be the best at 
discussing my future plans, but they have been an indispensible source of support during my time away from home. 
I am thankful to my lab members especially for adding brief moments of levity during my PhD and giving me the 
opportunity to be a part of their own journey in graduate school. Thank you to everyone who has been with me 
through thick and thin, and to many more celebrations of our achievements.

>>>>

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his methodical problem solving strategies, depth and 
breadth of knowledge have been invaluable sources of inspiration for me as well as 
motivation to strive towards those ideals. I would also like to thank members of my committee, 
from the University of Delaware and Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

Listing everyone I am grateful for who have provided me non-academic support would be too long for this page. 
I am grateful to my family, with whom I may not be the best at 
discussing my future plans, but they have been an indispensible source of support during my time away from home. 
I am thankful to my lab members especially for adding brief moments of levity during my PhD and giving me the 
opportunity to be a part of their own journey in graduate school. Thank you to everyone who has been with me 
through thick and thin, and to many more celebrations of our achievements.

### 2025-03-10 chapters/introduction.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcie et al. under license number 1548092-1. \cite{garcia_scalable_2019}}
    \label{fig:bijel_template}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. Reproduced from Adhikari et al. 
    under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 4]{figures/introduction/STrIPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 1]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields relevant in 
             water filtration and oil refining applications. Reproduced from Tham et al. 2021 under the ACS standard license \cite{tham_magnetophoresis_2021}}
    \label{fig:magnetophoresis_droplet}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. Reproduced from Davies et al. under the Creative Commons CC BY license \cite{davies_assembling_2014}}
    \label{fig:anisotropic_assembly}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcia et al. 
             Nanoscale Adv., 2019,1, 3870-3882 under license number 1548092-1. \cite{garcia_scalable_2019}}
    \label{fig:bijel_template}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 4]{figures/introduction/STrIPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
             the casting mixture through diffusion. \cite{haase_continuous_2015} Reproduced from Haase et al. Adv. Mater., 
             Volume27, Issue44, 2015, Pages 7065-7071 under license number 5913140219015. }
    \label{fig:strips}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 1]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. \cite{tham_magnetophoresis_2021} 
             Reproduced from Tham et al. Langmuir 2021, 37, 5, 1811-1822 under the ACS standard license.}
    \label{fig:magnetophoresis_droplet}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. \cite{davies_assembling_2014} Reproduced from Davies et al. Adv. Mater., 26: 6715-6719 under the 
             Creative Commons CC BY license.}
    \label{fig:anisotropic_assembly}
\end{figure}

### 2025-03-10 chapters/lit_review.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. 
    \cite{loudet_capillary_2005} Reproduced from Loudet et al. with license number RNP/25/FEB/088185}
    \label{fig:anisotropic_particle_interface}
\end{figure}

@@

Anisotropic particles have also been shown to exhibit natural liquid crystal like behaviour as shown using Onsager theory.

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. 
            Reproduced from Velankar 2015 using license number 1551968-1. \cite{velankar_non-equilibrium_2015}}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
             Reproduced from Bonaccorso et al. under the Creative Commons CC BY License. \cite{bonaccorso_shear_2020}}
    \label{fig:bijel_under_shear}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
             around the particle. \cite{loudet_capillary_2005} Reproduced from Loudet et al. Phys. Rev. Lett. 2005, 94, 018301
             with license number RNP/25/FEB/088185}
    \label{fig:anisotropic_particle_interface}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
            Reproduced from Velankar Soft Matter, 2015,11, 8393-8403 using license number 1551968-1.}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of 
             particles at the interface. \cite{bonaccorso_shear_2020} Reproduced from Bonaccorso et al. AIP Advances 1 
             September 2020; 10 (9): 095304, under the Creative Commons CC BY License.}
    \label{fig:bijel_under_shear}
\end{figure}

### 2025-03-10 chapters/paper1.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@

\begin{figure}
\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

>>>>

This section is based on work published in the Royal Society of Chemistry's Soft Matter journal and
work submited to the American Institude of Physics, Physics of Fluids journal. \cite{karthikeyan_formation_2024} 
It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry and 
reproduced from Ref [FULL CITATION], with the permission of AIP Publishing.

@@

\begin{figure}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

### 2025-03-10 chapters/paper2.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
through changes in pH, temperature, or chemical composition 
\cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.

@@

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q6 \rangle\).

We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
particle monolayers dictates the extent of microstructure evolution. Additionally, applying and removing a magnetic field results in distinct 
microstructural properties and timescales, highlighting the importance of processing history. These findings demonstrate how magnetic fields, 
combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.

>>>>

Sections of this chapter appear in a manuscript submitted to Springer link.
[author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
reproduced with permission of Palgrave Springer Nature.

% Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
% in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
% These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
% morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
% environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
% and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
% through changes in pH, temperature, or chemical composition 
% \cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.

@@

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
Steinhardt order parameter \(\langle Q6 \rangle\).

We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
particle monolayers dictates the extent of microstructure evolution if the applied field is increased. Additionally, applying and removing a 
magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
demonstrate how magnetic fields, combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.

### 2025-03-10 licenses/licenses.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

\begin{itemize}
    \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
    \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS): 5913140219015
    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
    Motion [Langmuir 2021, 37, 5, 1811-1822]: "Reprinted (adapted) with permission from 
    Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society."
    \item Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions [Adv. Mater., 26: 6715-6719]: Reproduced under the Creative Commons CC BY License.
    \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
    \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
    \item Shear dynamics of confined bijels [AIP Advances 1 September 2020; 10 (9): 095304]: Reproduced under the Creative Commons CC BY License.
    \item LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation of interacting amphiphilic fluids [Computer Physics Communications 2017, 217, 149--161]: Reproduced under the Creative Commons CC BY License
\end{itemize}

>>>>

\begin{itemize}
    \item E. Garcia, C. S. Wang, R. N. Sanderson, K. M. McDevitt, Y. Zhang, L. Valdevit, D. R.
    Mumm, A. Mohraz and R. Ragan. Scalable synthesis of gyroid-inspired freestanding three-
    dimensional graphene architectures. 1, 3870.: 1548092-1
    \item Stratford, R. Adhikari, I. Pagonabarraga, J.-C. Desplat and M. E. Cates. Colloidal jam-
    ming at interfaces: A route to fluid-bicontinuous gels. 309, 2198: 5966820525314
    \item F. Haase, K. J. Stebe and D. Lee. Continuous fabrication of hierarchical and asymmetric
    bijel microparticles, fibers, and membranes by solvent transfer-induced phase separation
    (STRIPS). 27, 7065: 5913140219015
    \item K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Mag-
    netophoresis of magnetic pickering emulsions under low field gradient: Macroscopic and
    microscopic motion. 37, 1811: "Reprinted (adapted) with permission from 
    Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society."
    \item G. B. Davies, T. Kr¨uger, P. V. Coveney, J. Harting and F. Bresme. Assembling ellipsoidal
    particles at fluid interfaces using switchable dipolar capillary interactions. 26, 6715.: Reproduced under the Creative Commons CC BY License.
    \item C. Loudet, A. M. Alsayed, J. Zhang and A. G. Yodh. Capillary interactions between
    anisotropic colloidal particles. 94, 018301: RNP/25/FEB/088185
    \item S. S. Velankar. A non-equilibrium state diagram for liquid/fluid/particle mixtures. 11, 8393: 1551968-1
    \item Bonaccorso, S. Succi, M. Lauricella, A. Montessori, A. Tiribocchi and K. H. Luo. Shear
    dynamics of confined bijels. 10, 095304.: Reproduced under the Creative Commons CC BY License.
    \item S. Schmieschek, L. Shamardin, S. Frijters, T. Kr¨uger, U. D. Schiller, J. Harting and P. V.
    Coveney. LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation
    of interacting amphiphilic fluids. Computer Physics Communications 217, 149 (2017).: Reproduced under the Creative Commons CC BY License
\end{itemize}
